---
title: "R code for LMO Tableau"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DiagrammeR)
library(tidyverse)
library(htmltools)
dfs <- readRDS("dataframes.RDS")
```


### Input Dataframes:

Here is a brief description of the input dataframes (column names, data type and an example)


```{r, echo=FALSE, results='asis'}
print_kable <- function(names, tbbl){
  cat(HTML(paste0("<h6> Input ",names,"</h6>")))
  tbbl%>%
    knitr::kable(escape = TRUE)%>%
    kableExtra::kable_styling("striped", position = "left", font_size = 7, full_width=FALSE)%>%
    print()
}

input_list <- dfs%>%
  filter(df_names %in% c("wages_raw",
                        "jo_raw",
                        "ind_char_raw",
                        "employment_raw",
                        "ds_raw",
                        "noc_mappings_raw",
                        "education_occupation_raw",
                        "hoo"))%>%
  deframe()

walk2(names(input_list), input_list, print_kable)
```

### Flowcharts for code:

##### Clean_JO.csv

```{r, echo=FALSE}
mermaid("
graph LR

2(JO single variables.csv)
3(Industry characteristics.xlsx)
4(Emp single variables.csv)

2 --> jo_raw
3 --> ind_char_raw
4 --> employment_raw

jo_raw --> job_openings
employment_raw --> employment_industry
ind_char_raw --> employment_industry

job_openings --> jo_employment
employment_industry --> jo_employment
jo_employment --> Clean_JO.csv

", height = '100%', width = '100%')
```

##### Supply_cleaned.csv

```{r, echo=FALSE}
mermaid("
graph LR

2(JO single variables.csv)
5(DS single variables.csv)

2 --> jo_raw
5 --> ds_raw

jo_raw --> jo_all_industries
jo_all_industries --> ds_merged
ds_raw --> ds_merged
ds_merged --> Supply_cleaned.csv
", height = '100%', width = '100%')
```

##### Occupations_regional.csv

```{r, echo=FALSE}
mermaid("
graph LR

2(JO single variables.csv)
3(Industry characteristics.xlsx)
4(Emp single variables.csv)
6(NOC Mappings.csv)
7(Occupation characteristics.xlsx)

2 --> jo_raw
3 --> ind_char_raw
4 --> employment_raw
6 --> noc_mappings_raw
7 --> education_occupation_raw

noc_mappings_raw --> noc_major_group
noc_mappings_raw --> noc_minor_group
noc_mappings_raw --> noc_unit
education_occupation_raw --> education_occupation
jobs_and_industry --> jobs_employment
education_occupation --> jobs_employment
jobs_employment --> occupation
occupation --> noccupation
noc_broad_occ --> noccupation
noc_major_group--> noccupation
noc_minor_group--> noccupation
noc_unit--> noccupation
noccupation --> Occupations_regional.csv
job_openings --> jo_employment
employment_industry --> jo_employment
jo_raw --> job_openings
ind_char_raw --> employment_industry
employment_raw --> employment_industry
ind_char_raw --> ind_char2
jo_employment --> jobs_and_industry
ind_char2 --> jobs_and_industry
noc_mappings_raw --> noc_broad_occ
", height = '100%', width = '100%')
```
##### Jobs_and_industry.csv 
```{r, echo=FALSE}
mermaid("
graph LR
1(Industry characteristics.xlsx)
2(JO single variables.csv)
3(Emp single variables.csv)
4(NOC Mappings.csv)
5(Occupation characteristics.xlsx)

1 --> ind_char_raw
2 --> jo_raw
3 --> employment_raw
4 --> noc_mappings_raw
5 --> education_occupation_raw

noc_unit --> noccupation
ind_char_raw --> ind_char2
job_openings --> jo_employment
noccupation --> noc_mappings2
ind_char2 --> jobs_and_industry
jo_employment --> jobs_and_industry
jobs_and_industry --> jobs_industry_noc
noc_mappings2 --> jobs_industry_noc
jobs_industry_noc --> Jobs_and_Industry.csv
employment_raw --> employment_industry
ind_char_raw --> employment_industry
employment_industry --> jo_employment
education_occupation_raw --> education_occupation
noc_mappings_raw --> noc_broad_occ
noc_mappings_raw --> noc_major_group
noc_mappings_raw --> noc_minor_group
noc_mappings_raw --> noc_unit
education_occupation --> jobs_employment
jobs_and_industry --> jobs_employment
jobs_employment --> occupation
jo_raw --> job_openings
occupation --> noccupation
noc_broad_occ --> noccupation
noc_major_group--> noccupation
noc_minor_group--> noccupation
", height = '100%', width = '100%')
```

##### Employment_Growth_Rates.csv 
```{r, echo=FALSE}
mermaid("
graph LR

1(JO single variables.csv)
2(Industry characteristics.xlsx)
3(Emp single variables.csv)
4(Occupation characteristics.xlsx)
5(NOC Mappings.csv)

1 --> jo_raw
2 --> ind_char_raw
3 --> employment_raw
4 --> education_occupation_raw
5 --> noc_mappings_raw

noc_mappings_raw --> noc_broad_occ
noc_mappings_raw --> noc_major_group
noc_mappings_raw --> noc_minor_group
noc_mappings_raw --> noc_unit
jobs_employment --> occupation
occupation --> noccupation
noc_broad_occ --> noccupation
noc_major_group--> noccupation
noc_minor_group--> noccupation
noc_unit--> noccupation
jo_raw --> job_openings
employment_raw --> employment_industry
ind_char_raw --> employment_industry
job_openings --> jo_employment
employment_industry --> jo_employment
ind_char_raw --> ind_char2
noccupation --> noc_mappings2
education_occupation_raw --> education_occupation
jo_employment --> jobs_and_industry
ind_char2 --> jobs_and_industry
jobs_and_industry --> jobs_industry_noc
noc_mappings2 --> jobs_industry_noc
education_occupation --> jobs_employment
jobs_and_industry --> jobs_employment
jobs_industry_noc --> mapping
jobs_employment --> by_aggregated_industry
jobs_employment --> by_individual_industry
mapping --> by_individual_industry
by_individual_industry --> individual_industry_agg_industry
by_aggregated_industry --> individual_industry_agg_industry
individual_industry_agg_industry --> Employment_Growth_Rates.csv
", height = '100%', width = '100%')
```






##### occ_characteristics_wage.csv

```{r, echo=FALSE}
mermaid("
graph LR

1(JO single variables.csv) 
2(Emp single variables.csv) 
3(Industry characteristics.xlsx) 
4(2020Preliminary wages.xlsx)
5(Occupation characteristics.xlsx)

1 --> jo_raw
2 --> employment_raw
3 --> ind_char_raw
4 --> wages_raw
5 --> education_occupation_raw

jo_raw --> job_openings
employment_raw -->employment_industry
ind_char_raw --> employment_industry
job_openings --> jo_employment
employment_industry --> jo_employment
ind_char_raw --> ind_char2
wages_raw --> wages_cleaned
jo_employment --> jobs_and_industry
ind_char2 --> jobs_and_industry
education_occupation_raw --> education_occupation
education_occupation_raw --> occ_group
jobs_and_industry --> jobs_employment
education_occupation --> jobs_employment
wages_cleaned --> group_and_wages
occ_group --> group_and_wages
education_occupation_raw --> occ_characteristics
jobs_employment --> j_openings
jobs_employment --> emp
group_and_wages --> group_wages_characteristics
occ_characteristics --> group_wages_characteristics
j_openings --> group_wages_characteristics
emp --> group_wages_characteristics
group_wages_characteristics --> occ_characteristics_wage.csv
", height = '100%', width = '100%')
```

### Output dataframe summaries:

Here is a brief description of the output dataframes (column names, data type and an example)


```{r, echo=FALSE, results='asis'}
print_kable <- function(names, tbbl){
  cat(HTML(paste0("<h6> Output ",names,"</h6>")))
  tbbl%>%
    knitr::kable(escape = TRUE)%>%
    kableExtra::kable_styling("striped", position = "left", font_size = 7, full_width=FALSE)%>%
    print()
}

out_list <- dfs%>%
  filter(df_names %in% c("jo_employment",
                        "ds_merged",
                        "occupation",
                        "jobs_industry_noc",
                        "individual_industry_agg_industry",
                        "group_wages_characteristics"))%>%
  deframe()

walk2(names(out_list), out_list, print_kable)
```


