---
title: "2022 B.C. Labour Market Outlook"
output:
  flexdashboard::flex_dashboard:
    orientation: columns
runtime: shiny
css: style.css
resource_files:
- shiny_data/long.csv
---
```{r}
library(tidyverse)
library(shinyWidgets)
library(plotly)
long <- read_csv(here::here("shiny_data","long.csv"))%>%
  rename(Geographic_Area=`Geographic Area`)%>% #selectizeGroupUI cant handle non-syntactic names
  mutate(Geographic_Area=fct_reorder(Geographic_Area, value, max))

page_titles <- c("Landing Page",
                 "Highlights Part 1",
                 "Annual Outlook",
                 "Regional Outlook",
                 "Industry Outlook",
                 "Occupational Outlook",
                 "Industry Outlook Data Table",
                 "Occupational Outlook Data Table",
                 "High Opportunity Occupations",
                 "Job Openings 500 Occupations",
                 "Sources of New Supply",
                 "Labour Market Definitions")


nav_but <- function(direction, current_page){
    if(direction=="previous"){
      if(current_page==1){
        name = tail(page_titles, n=1)
      }else{
        name = page_titles[current_page-1]
      }
    }
  if(direction == "next"){
      if(current_page == length(page_titles)){
        name = page_titles[1]
      }else{
        name = page_titles[current_page+1]
      }
    }
  name <- str_to_lower(name)%>%
      str_replace_all(" ","-")
  lab <-  str_to_title(paste(direction, "Page"))
  oc <- paste0("location.href='#section-",name,"';")
  actionButton("1", label = lab, class = "btn btn-sm btn-primary", 
            onclick = oc)
}

```

`r page_titles[1]` {data-navmenu="Table of Contents"}
=====================================
Inputs {.sidebar}
-------------------------------------
```{r}
nav_but(direction = "previous", current_page = 1)
nav_but(direction = "next", current_page = 1)
```

Column
-------------------------------------
### `r page_titles[1]`

`r page_titles[2]`  {data-navmenu="Table of Contents"}
===========================================
Inputs {.sidebar}
-------------------------------------
```{r}
nav_but(direction = "previous", current_page = 2)
nav_but(direction = "next", current_page = 2)

```

Column 
-------------------------------------
### `r page_titles[2]`

`r page_titles[3]`  {data-navmenu="Table of Contents"}
===========================================
Inputs {.sidebar}
-------------------------------------
```{r}
nav_but(direction = "previous", current_page = 3)
nav_but(direction = "next", current_page = 3)

```

Column
-------------------------------------
### `r page_titles[3]`

`r page_titles[4]`  {data-navmenu="Table of Contents"}
=========================================
Inputs {.sidebar}
-------------------------------------
```{r}
nav_but(direction = "previous", current_page = 4)
nav_but(direction = "next", current_page = 4)

```

Column
-------------------------------------
### `r page_titles[4]`

`r page_titles[5]` {data-navmenu="Table of Contents"}
=========================================
Inputs {.sidebar}
-------------------------------------
```{r}
nav_but(direction = "previous", current_page = 5)
nav_but(direction = "next", current_page = 5)

```

Column
-------------------------------------
### `r page_titles[5]`

`r page_titles[6]`  {data-navmenu="Table of Contents"}
========================================
Inputs {.sidebar}
-------------------------------------

### Navigation

```{r}
nav_but(direction = "previous", current_page = 6)
nav_but(direction = "next", current_page = 6)
```

### Inputs

```{r}
selectizeGroupUI(
        id = "my-filters",
        inline = FALSE,
        params = list(
          var_one = list(inputId = "name", title = "Choose a Variable", placeholder = "select"),
          var_two = list(inputId = "Geographic_Area", title = "Choose a Geographic Area", placeholder = "select"),
          var_three = list(inputId = "NOC1", title = "Choose a NOC1", placeholder = "select"),
          var_four = list(inputId = "NOC2", title = "Choose a NOC2", placeholder = "select"),
          var_five = list(inputId = "NOC3", title = "Choose a NOC3", placeholder = "select")
        )
      )

res_mod <- callModule(
    module = selectizeGroupServer,
    id = "my-filters",
    data = long,
    vars = c(
      "name",
      "Geographic_Area",
      "NOC1",
      "NOC2",
      "NOC3"
    )
)

noc_agg <- reactive({
  case_when(is.null(input[["my-filters-NOC1"]]) & 
           is.null(input[["my-filters-NOC2"]]) &
           is.null(input[["my-filters-NOC3"]]) ~ "NOC1",
           is.null(input[["my-filters-NOC2"]]) & 
           is.null(input[["my-filters-NOC3"]]) ~ "NOC2",
           is.null(input[["my-filters-NOC3"]]) ~ "NOC3",
           TRUE~"NOC4")
})

tbbl <- reactive({
  res_mod()%>%
    distinct(Geographic_Area, name, get(noc_agg()), .keep_all = TRUE)%>%
    select(Geographic_Area, name, value, noc="get(noc_agg())")%>%
    na.omit()
})


```

Column
-------------------------------------------

### `r page_titles[6]` 

```{r fig.retina=2}
renderPlotly({
  plt <- tbbl()%>%
    ggplot(aes(value,
               fct_reorder(noc, value, .fun = max),
               fill=Geographic_Area,
               text= paste0(
                "Geographic Area: ", Geographic_Area, "\n",
                "NOC: ", noc, "\n",
                "Value: ", scales::comma(value, accuracy = .01))
               ))+
    geom_col(position = "dodge2")+
    scale_x_continuous(labels = scales::comma)+
    scale_fill_viridis_d()+
    facet_wrap(vars(name), scales = "free_x")+
    labs(x="",y="")+
    guides(fill = guide_legend(reverse=TRUE))+
    theme_minimal()+
    theme(axis.text.x = element_text(angle = 15))
  ggplotly(plt, tooltip="text")%>%
    config(displayModeBar = F)
})
```

`r page_titles[7]`  {data-navmenu="Table of Contents"}
========================================
Inputs {.sidebar}
-------------------------------------
```{r}
nav_but(direction = "previous", current_page = 7)
nav_but(direction = "next", current_page = 7)
```

Column
-------------------------------------
### `r page_titles[7]`

`r page_titles[8]` {data-navmenu="Table of Contents"}
========================================
Inputs {.sidebar}
-------------------------------------
```{r}
nav_but(direction = "previous", current_page = 8)
nav_but(direction = "next", current_page = 8)

```

Column
-------------------------------------
### `r page_titles[8]`

`r page_titles[9]` {data-navmenu="Table of Contents"}
========================================
Inputs {.sidebar}
-------------------------------------
```{r}
nav_but(direction = "previous", current_page = 9)
nav_but(direction = "next", current_page = 9)
```

Column
-------------------------------------
### `r page_titles[9]`

`r page_titles[10]`  {data-navmenu="Table of Contents"}
========================================
Inputs {.sidebar}
-------------------------------------
```{r}
nav_but(direction = "previous", current_page = 10)
nav_but(direction = "next", current_page = 10)
```

Column
-------------------------------------
### `r page_titles[10]`

`r page_titles[11]`  {data-navmenu="Table of Contents"} 
=========================================
Inputs {.sidebar}
-------------------------------------
```{r}
nav_but(direction = "previous", current_page = 11)
nav_but(direction = "next", current_page = 11)
```

Column
-------------------------------------
### `r page_titles[11]` 

`r page_titles[12]`  {data-navmenu="Table of Contents"}
=========================================
Inputs {.sidebar}
-------------------------------------
```{r}
nav_but(direction = "previous", current_page = 12)
nav_but(direction = "next", current_page = 12)
```

Column
-------------------------------------
### `r page_titles[12]` 




